Happiness Does Not Cause Altruism: A review of US General Social Survey data

### 2023-03-16 outputs/paper/paper.qmd
Major updates
* Updated comments and metadata throughout project
* Updated readme files throughout project
* Added tests for the data
* Added data simulation

```{r}
#| messages: false
#| echo: false
#| warning: false
#| output: false
#### Preamble ####
# Title: Does Happiness Lead to Altruism: A review of US General Social Survey data
# Author: Sebastian Rodriguez, Randall Ni, Iz Leitch
# Email: me@srod.ca
# Date: 16 March 2023
# GitHub: https://github.com/seb646/happiness-and-altruism

@@

# Fetch the the clean response data
happy_positive_data <- readr::read_csv(here::here("inputs/data/clean/happy_positive_data.csv"), show_col_types = FALSE)

# Fetch clean performance data
directions_positive_data <- readr::read_csv(here::here("inputs/data/clean/directions_positive_data.csv"), show_col_types = FALSE)

# Fetch the clean incident response
homeless_positive_data <- readr::read_csv(here::here("inputs/data/clean/homeless_positive_data.csv"), show_col_types = FALSE)

# Fetch the the clean response data
happy_negative_data <- readr::read_csv(here::here("inputs/data/clean/happy_negative_data.csv"), show_col_types = FALSE)

# Fetch clean performance data
directions_negative_data <- readr::read_csv(here::here("inputs/data/clean/directions_negative_data.csv"), show_col_types = FALSE)

# Fetch the clean incident response
homeless_negative_data <- readr::read_csv(here::here("inputs/data/clean/homeless_negative_data.csv"), show_col_types = FALSE)
```

@@

colors <- c(
  'Feeling "pretty happy" or "very happy"' = "steelblue",
  "Giving money or food to the homeless\n more than 2 times a year" = "darkred"
)

@@

  geom_line(data = happy_positive_data, aes(x = year, y = people, color = 'Feeling "pretty happy" or "very happy"')) +
  geom_line(data = homeless_positive_data, aes(x = year, y = people, color = "Giving money or food to the homeless\n more than 2 times a year")) +
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +
  scale_color_manual(values = colors)
```

@@

colors <- c(
  'Feeling "not to happy"' = "steelblue",
  "Giving money or food to the homeless\n less than 2 times a year" = "darkred"
)

@@

  geom_line(data = happy_negative_data, aes(x = year, y = people, color = 'Feeling "not to happy"')) +
  geom_line(data = homeless_negative_data, aes(x = year, y = people, color =  "Giving money or food to the homeless\n less than 2 times a year")) +
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +
  scale_color_manual(values = colors)
```

@@

colors <- c(
  'Feeling "pretty happy" or "very happy"' = "steelblue",
  "Giving directions to a stranger\n more than 2 times a year" = "darkred"
)

@@

  geom_line(data = happy_positive_data, aes(x = year, y = people, color = 'Feeling "pretty happy" or "very happy"')) +
  geom_line(data = directions_positive_data, aes(x = year, y = people, color = "Giving directions to a stranger\n more than 2 times a year")) +
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +
  scale_color_manual(values = colors)
```

@@

colors <- c(
  'Feeling "not too happy"' = "steelblue",
  "Giving directions to a stranger\n less than 2 times a year" = "darkred"
)

@@

  geom_line(data = happy_negative_data, aes(x = year, y = people, color = 'Feeling "not too happy"')) +
  geom_line(data = directions_negative_data, aes(x = year, y = people, color = "Giving directions to a stranger\n less than 2 times a year")) +
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +
  scale_color_manual(values = colors)
```

>>>>

```{r}
#| messages: false
#| echo: false
#| warning: false
#| output: false
#### Preamble ####
# Title: Happiness Does Not Cause Altruism: A review of US General Social Survey data
# Author: Sebastian Rodriguez, Randall Ni, Iz Leitch
# Email: me@srod.ca
# Date: 16 March 2023
# GitHub: https://github.com/seb646/happiness-and-altruism

@@

# Fetch the the clean happiness positive data
happy_positive_data <- readr::read_csv(here::here("inputs/data/clean/happy_positive_data.csv"), show_col_types = FALSE)

# Fetch clean directions positive data
directions_positive_data <- readr::read_csv(here::here("inputs/data/clean/directions_positive_data.csv"), show_col_types = FALSE)

# Fetch the clean homeless positive data
homeless_positive_data <- readr::read_csv(here::here("inputs/data/clean/homeless_positive_data.csv"), show_col_types = FALSE)

# Fetch the the clean happy negative data
happy_negative_data <- readr::read_csv(here::here("inputs/data/clean/happy_negative_data.csv"), show_col_types = FALSE)

# Fetch clean directions negative data
directions_negative_data <- readr::read_csv(here::here("inputs/data/clean/directions_negative_data.csv"), show_col_types = FALSE)

# Fetch the clean homeless negative data
homeless_negative_data <- readr::read_csv(here::here("inputs/data/clean/homeless_negative_data.csv"), show_col_types = FALSE)
```

@@

# Set the colors for the lines and labels for the legend
colors <- c(
  'Feeling "pretty happy" or "very happy"' = "steelblue",
  "Giving money or food to the homeless\n more than 2 times a year" = "darkred"
)

@@

  # Import the happy positive data for the line
  geom_line(data = happy_positive_data, aes(x = year, y = people, color = 'Feeling "pretty happy" or "very happy"')) +

  # Import the homeless positive data for the line
  geom_line(data = homeless_positive_data, aes(x = year, y = people, color = "Giving money or food to the homeless\n more than 2 times a year")) +

  # Set scales to only be years where data is provided
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +

  # Set colors for the graph
  scale_color_manual(values = colors)
```

@@

# Set the colors for the lines and labels for the legend
colors <- c(
  'Feeling "not to happy"' = "steelblue",
  "Giving money or food to the homeless\n less than 2 times a year" = "darkred"
)

@@

  # Import the happy negative data for the line
  geom_line(data = happy_negative_data, aes(x = year, y = people, color = 'Feeling "not to happy"')) +

  # Import the homeless negative data for the line
  geom_line(data = homeless_negative_data, aes(x = year, y = people, color =  "Giving money or food to the homeless\n less than 2 times a year")) +

  # Set scales to only be years where data is provided
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +

  # Set colors for the graph
  scale_color_manual(values = colors)
```

@@

# Set the colors for the lines and labels for the legend
colors <- c(
  'Feeling "pretty happy" or "very happy"' = "steelblue",
  "Giving directions to a stranger\n more than 2 times a year" = "darkred"
)

@@

  # Import the happy positive data for the line
  geom_line(data = happy_positive_data, aes(x = year, y = people, color = 'Feeling "pretty happy" or "very happy"')) +

  # Import the directions positive data for the line
  geom_line(data = directions_positive_data, aes(x = year, y = people, color = "Giving directions to a stranger\n more than 2 times a year")) +

  # Set scales to only be years where data is provided
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +

  # Set colors for the graph
  scale_color_manual(values = colors)
```

@@

# Set the colors for the lines and labels for the legend
colors <- c(
  'Feeling "not too happy"' = "steelblue",
  "Giving directions to a stranger\n less than 2 times a year" = "darkred"
)

@@

  # Import the happy negative data for the line
  geom_line(data = happy_negative_data, aes(x = year, y = people, color = 'Feeling "not too happy"')) +

  # Import the directions negative data for the line
  geom_line(data = directions_negative_data, aes(x = year, y = people, color = "Giving directions to a stranger\n less than 2 times a year")) +

  # Set scales to only be years where data is provided
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +

  # Set colors for the graph
  scale_color_manual(values = colors)
```
